\newcommand{\cm}{card master}
\newcommand{\CM}{Card Master}

\clearpage
\section{Class - \CM(WT)}
\todo[inline]{Lore - intro}

\subsection{Lore1}
\todo[inline]{Lore}

\subsection{Lore2}
\todo[inline]{Lore}

\subsection{Creating a \CM}
\todo[inline]{Lore - How to play a \cm}

\subsubsection{Quick build}
You can make a \cm{} quickly by following these
suggestions. First, make Charisma, Wisdom or Intelligence your
highest ability score, depending on whether you
want to focus on ARCHETYPE1, ARCHETYPE2 or ARCHETYPE3, followed by Constitution. Second, choose the
**** background.

\subsection{Class features}
As a \cm, you gain the following class features.

\subsubsection{Hit Points}
\textbf{Hit Dice:} 1d6 per \cm level \\
\textbf{Hit Points at 1st Level:} 6 + your Constitution modifier \\
\textbf{Hit Points at Higher Level:} Id6 (or 4) + your
Constitution modifier per \cm level after 1st \\

\subsubsection{Proficiencies}
\todo[inline]{Figure out Proficiencies, make them balanced, especially saving throws}
\textbf{Armor:} None \\
\textbf{Weapons:} Daggers, darts, slings, quarterstaffs,
light crossbows \\
\todo[inline]{Definitely have proficiency in playing cards :P}
\textbf{Tools:} Playing Cards \\
\textbf{Saving Throws:} Constitution, Charisma \\
\textbf{Skills:} Choose two from Arcana, Deception, Insight,
Intimidation, Persuasion, and Religion \\

\subsubsection{Equipment}
You start with the following equipment, in addition to
the equipment granted by your background:
\begin{itemize}
	\item (a) a light crossbow and 20 bolts or (b) any simple weapon
	\item (a) a component pouch or (b) an arcane focus
	\item (a) a dungeoneer's pack or (b) an explorer's pack Two daggers
\end{itemize}

\subsection{A Set of Cards}
You have acquired or been given a magical set of cards. This set of cards will determine 

\section{Set of cards}

\subsection{Elemental Cards- WT}
\todo[inline]{Int Based - Planning and combo deck}

\subsection{Wild Cards - WT}
\todo[inline]{Cha Based - Rush and Card draw}
Special resource, wild cards. Can work as a copy of any card but has wild magic consequences.

\subsection{Tarot Cards}
\todo[inline]{Wis Based - Deck manipulation trough prediction?}